Arc Blanc: a real time ocean simulation framework

### 2025-02-04 paper.tex
Add figure to clarify the desired mask

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Evaluate the height of vertices in the mask}
\label{subsubsec:heightMask}
Knowing all the vertices in the mask, their height must be given as input of the FDM.
\Framework uses a simple model that tries to reproduce parts of the idea of Cords and Staadt (2009) \cite{cordsRealTimeOpenWater2009}.
By construction of the grid $Z$, $M$ has its bow oriented on the positive side of the $z$ axis, and its starboard (right-hand side when facing the bow) on the positive side of the $x$ axis.
Hence, $h$ is made such that from the vertex at position $\mathbf x$, the front of the mask is above the free surface and the back below, in a way that is proportional to the speed of $M$.
Moreover, the boat forms a $V$ shape, with its center a bit below the extremity of the side.

@@

	\subfloat[A theoretical view of the height of the mask, with input a simple rectangle.]
	{
		\includegraphics[width=0.25\textwidth]{Figures/Mask3D_theoric_view.png}
		\label{subfig:maskTheoreticalView}
	}
	\hspace{1cm}
	\subfloat[The height of the mask of a simple boat encoded in a single channel texture.]
	{
		\includegraphics[width=0.25\textwidth]{Figures/MaskHeightMap.png}
		\label{subfig:maskHeightMap}
	}
	\hspace{1cm}
	\subfloat[The height of the mask of a simple boat in a 3D scene with a very low sea state. Boat rendering and wave propagation has been disabled to only display the initial step of the height of the mask.]
	{
		\includegraphics[width=0.25\textwidth]{Figures/Mask3D-contrast.png}
		\label{subfig:mask3D}
	}
	\caption{Three different views of the height of the mask defined by Equation \ref{equa:mask_full}.}
	\label{fig:mask}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Evaluate the height of vertices in the mask}
\label{subsubsec:heightMask}
Knowing all the vertices in the mask, their height must be given as input of the FDM.
\Framework uses a simple model that tries to reproduce parts of the idea of Cords and Staadt (2009) \cite{cordsRealTimeOpenWater2009}.
By construction of the grid $Z$, $M$ has its bow oriented on the positive side of the $z$ axis, and its starboard (right-hand side when facing the bow) on the positive side of the $x$ axis.
Hence, $h$ is made such that from the vertex at position $\mathbf x$, the front of the mask is above the free surface and the back below, in a way that is proportional to the speed of $M$.
Moreover, the boat forms a $V$ shape laterally, with its center a bit below the extremity of the side. Figure \ref{fig:mask_maskTheoreticalView} presents the desired shape from three different perspectives.

	\subfloat[Three quarter view]
	{
		\includegraphics[width=0.25\textwidth]{Figures/mask_diagonal_view.png}
	}
	\hspace{1cm}
	\subfloat[Back view]
	{
		\includegraphics[width=0.25\textwidth]{Figures/mask_back_view.png}
	}
	\hspace{1cm}
	\subfloat[Side view]
	{
		\includegraphics[width=0.25\textwidth]{Figures/mask_side_view.png}
	}
	\caption{Three different theoretical point of view of the mask for a simple rectangle.}
	\label{fig:mask_maskTheoreticalView}
\end{figure}

@@

\begin{figure}[htbp]
	\centering
	\subfloat[The height of the mask of a simple boat encoded in a single channel texture.]
	{
		\includegraphics[width=0.25\textwidth]{Figures/MaskHeightMap.png}
		\label{subfig:maskHeightMap}
	}
	\hspace{1cm}
	\subfloat[The height of the mask of a simple boat in a 3D scene with a very low sea state. Boat rendering and wave propagation has been disabled to only display the initial step of the height of the mask.]
	{
		\includegraphics[width=0.25\textwidth]{Figures/Mask3D-contrast.png}
		\label{subfig:mask3D}
	}
	\caption{Two different views of the height of the mask defined by Equation \ref{equa:mask_full} for a simple boat.}
	\label{fig:mask}
\end{figure}
